---
title: "APIM"
author: "Emma Livingston"
date: "11/29/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(psysds364data)
library(tidyverse)
library(psych)
library(nlme)
library(mosaic)

```

Run the data_wrangling.Rmd so you have `pairwise` in your environment.

# Basic model

## Indistinguishable Dyads

Here we have a model where gender of the actor and gender of the partner predict the perceived social competence of the child for the actor. 

I attempted to create a model where the gender of the actor and the gender of the partner are interacted with group (so that we have gender and sexual orientation in the model), but I get an error (Error in glsEstimate(object, control = control) : computed "gls" fit is singular, rank 5).

```{r baseline_model}
apim <- gls(soc_comp_a ~ gender_e_a + gender_e_p,
            data = pairwise,
            correlation = corCompSymm(form = ~1|id),
            na.action = na.omit)

summary(apim)

apim_intact <- gls(soc_comp_a ~ gender_e_a:group + gender_e_p:group,
            data = pairwise,
            correlation = corCompSymm(form = ~1|id),
            na.action = na.omit)

summary(apim_intact)
```

ICC just gender: 0.6747253
ICC gender and group: 0.6775821

## Calculate R^2^

Calculate R-squared by taking the SSE of the model, dividing by the SSE of the empty model, and subtracting that from 1. Our baseline model does very very poorly. 

```{r apim_empty}
apim_empty <- gls(soc_comp_a ~ 1,
                  data = pairwise,
                  correlation = corCompSymm(form = ~1|id),
                  na.action = na.omit)
summary(apim_empty)

r2_gender <- 1-(apim$sigma^2/apim_empty$sigma^2)
r2_gender
```

```{r r2_intact}
r2_intact <- 1 - (apim_intact$sigma^2/apim_empty$sigma^2)
r2_intact
```
yikes this isn't going well

## Interpretation of Model Estimates

* *Intercept*: meaningless because not centered

* *actor variable*: I truly don't understand how to interpret this right now

* *partner variable*:
 

# Moderator 

We first center the moderator and predictor variables:

```{r}
pairwise <- pairwise %>%
  mutate(h12selfdir_a_ctr = h12selfdir_a - mean(h12selfdir_a),
         h12selfdir_p_ctr = h12selfdir_p - mean(h12selfdir_p),
         soc_comp_a_ctr = soc_comp_a - mean(soc_comp_a),
         soc_comp_p_ctr = soc_comp_p - mean(soc_comp_p))

pairwise <- pairwise %>%
  mutate(samesex = ifelse(group == 1 | group == 2, 1, 0))

```

We then estimate the two-intercept model:

```{r}
# moderation <- gls(soc_comp_a ~ 
#                     h12selfdir_a_ctr:gender_e_a:group +
#                     h12selfdir_a_ctr:gender_e_p:group +
#                     h12selfdir_p_ctr:gender_e_a:group +
#                     h12selfdir_p_ctr:gender_e_p:group,
#                   data = pairwise,
#                   correlation = corCompSymm(form = ~1|id),
#                   na.action = na.omit)
# 
# summary(moderation)
# coef(summary(moderation))

# #Randi added
# #actor gender by partner gender
# moderation <- gls(soc_comp_a ~ gender_e_a:gender_e_p +
#                     h12selfdir_a_ctr:gender_e_a:gender_e_p +
#                     h12selfdir_p_ctr:gender_e_p:gender_e_p,
#                   data = pairwise,
#                   correlation = corCompSymm(form = ~1|id),
#                   na.action = na.omit)
# 
# summary(moderation)
# coef(summary(moderation))
# 
# #actor gender by samesex (indicator variable)
# moderation <- gls(soc_comp_a ~ gender_e_a:samesex +
#                     h12selfdir_a_ctr:gender_e_a:samesex +
#                     h12selfdir_p_ctr:gender_e_p:samesex,
#                   data = pairwise,
#                   correlation = corCompSymm(form = ~1|id),
#                   na.action = na.omit)
# 
# summary(moderation)
# coef(summary(moderation))

#simply use the group variable
moderation <- gls(soc_comp_a ~ as.factor(group) +
                    h12selfdir_a_ctr:as.factor(group) +
                    h12selfdir_p_ctr:as.factor(group) - 1,
                  data = pairwise,
                  correlation = corCompSymm(form = ~1|id),
                  na.action = na.omit)

summary(moderation)
coef(summary(moderation))

moderation <- gls(soc_comp_a ~ as.factor(samesex) +
                    h12selfdir_a_ctr:as.factor(samesex) +
                    h12selfdir_p_ctr:as.factor(samesex) - 1,
                  data = pairwise,
                  correlation = corCompSymm(form = ~1|id),
                  na.action = na.omit)

summary(moderation)
coef(summary(moderation))

moderation <- gls(soc_comp_a ~ h12selfdir_a_ctr*as.factor(samesex) +
                    h12selfdir_p_ctr*as.factor(samesex),
                  data = pairwise,
                  correlation = corCompSymm(form = ~1|id),
                  na.action = na.omit)

summary(moderation)

coef(summary(moderation))
```

```{r conformity}
# moderation <- gls(soc_comp_a ~ as.factor(group) +
#                     h12conform_a_ctr:as.factor(group) +
#                     h12conform_p_ctr:as.factor(group) - 1,
#                   data = pairwise,
#                   correlation = corCompSymm(form = ~1|id),
#                   na.action = na.omit)
# 
# summary(moderation)
# coef(summary(moderation))
# 
# moderation <- gls(soc_comp_a ~ as.factor(samesex) +
#                     h12conform_a_ctr:as.factor(samesex) +
#                     h12conform_p_ctr:as.factor(samesex) - 1,
#                   data = pairwise,
#                   correlation = corCompSymm(form = ~1|id),
#                   na.action = na.omit)
# 
# summary(moderation)
# coef(summary(moderation))
# 
# moderation <- gls(soc_comp_a ~ h12conform_a_ctr*as.factor(samesex) +
#                     h12conform_p_ctr*as.factor(samesex),
#                   data = pairwise,
#                   correlation = corCompSymm(form = ~1|id),
#                   na.action = na.omit)
# 
# summary(moderation)
# 
# coef(summary(moderation))
```


```{r}
pairwise <- pairwise %>%
  mutate(h12selfdir_a_ctrhigh = h12selfdir_a_ctr - sd(h12selfdir_a_ctr),
         h12selfdir_p_ctrhigh = h12selfdir_p_ctr - sd(h12selfdir_p_ctr),
         h12selfdir_a_ctrlow = h12selfdir_a_ctr + sd(h12selfdir_a_ctr),
         h12selfdir_p_ctrlow = h12selfdir_p_ctr + sd(h12selfdir_p_ctr))

```

```{r}
a_high <- gls(soc_comp_a ~ as.factor(group) +
                h12selfdir_a_ctrhigh:as.factor(group) +
                h12selfdir_p_ctr:as.factor(group) - 1,
              data = pairwise,
              correlation = corCompSymm(form = ~1|id))

summary(a_high)

a_low <- gls(soc_comp_a ~ as.factor(group) +
                h12selfdir_a_ctrlow:as.factor(group) +
                h12selfdir_p_ctr:as.factor(group) - 1,
              data = pairwise,
              correlation = corCompSymm(form = ~1|id))

summary(a_low)

p_high <- gls(soc_comp_a ~ as.factor(group) +
                h12selfdir_a_ctr:as.factor(group) +
                h12selfdir_p_ctrhigh:as.factor(group) - 1,
              data = pairwise,
              correlation = corCompSymm(form = ~1|id))

summary(p_high)

p_low <- gls(soc_comp_a ~ as.factor(group) +
                h12selfdir_a_ctr:as.factor(group) +
                h12selfdir_p_ctrlow:as.factor(group) - 1 ,
              data = pairwise,
              correlation = corCompSymm(form = ~1|id))

summary(p_low)
```

