---
title: "Untitled"
author: "Emma Livingston"
date: "10/23/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_data}
library(psysds364data)
library(tidyverse)
library(sjlabelled)
library(psych)
library(skimr)
data("Goldberg_gav")
```

```{r variables}
var_labels <- data.frame(column_name = colnames(Goldberg_gav),
                         variable_label = sjlabelled::get_label(Goldberg_gav))

Goldberg_gav_sm <- Goldberg_gav %>%
  select(ID,
         Partner,
         group,
         ChildAge,
         chgend,
         gendexp,
         gender,
         sexor,
         w11RelDur,
         contains("chrace"),
         religion,
         howrelig,
         contains("otherch"),
         occup,
         contains("otherwork"),
         educ,
         faminc,
         paraccme_5,
         contains("polit"),
         contains("gayaff"),
         cityst,
         contains("genderparent"),
         sexor,
         contains("myrace"),
         contains("h12"),
         contains("w12"),
         h12social,
         h12selfdir,
         h12conform,
         contains("soccomp"),
         SocComp,
         Prosocial,
         Emotional
         )

```

```{r subset_data}
#exclude individuals who do not have data for parental values or social competence

#find the subset of dyads who have information for both people for all of the variables
Goldberg_gav_completes <- Goldberg_gav_sm %>%
  filter(!is.na(SocComp) & !is.na(Prosocial) & !is.na(Emotional) & !is.na(h12social) & !is.na(h12selfdir) & !is.na(h12conform)) %>%
  group_by(ID) %>%
  count() %>%
  filter(n == 2)

#join this subset with the full set of individuals
Goldberg_gav_sm <- Goldberg_gav_sm %>%
  inner_join(Goldberg_gav_completes, by = "ID")

```



```{r}
Goldberg_gav_sm %>%
  group_by(gender) %>%
  count()



Goldberg_gav_sm %>%
  group_by(gender) %>%
  count()

#impute ID 231 partner 2's relationship duration
Goldberg_gav_sm <- Goldberg_gav_sm %>%
  mutate(w11RelDur = ifelse(ID == 231 & Partner == 2, 7.0, w11RelDur))
  
```

```{r write_csv}
#write_csv(Goldberg_gav_sm, "C:/Users/livin/Documents/Smith Senior Year/Intergroup Relationships/Research Project/Goldberg_gav_sm.csv")
```


```{r subset_by_group}
lesbians <- Goldberg_gav_sm %>%
  filter(group == 1)

gays <- Goldberg_gav_sm %>%
  filter(group == 2)

straight_men <- Goldberg_gav_sm %>%
  filter(group == 3 & gender == 2)

straight_women <- Goldberg_gav_sm %>%
  filter(group == 3 & gender == 1)
```

```{r averages}

mean(lesbians$SocComp)
mean(gays$SocComp)
mean(straight_men$SocComp)
mean(straight_women$SocComp)

mean(lesbians$h12conform)
mean(gays$h12conform)
mean(straight_men$h12conform)
mean(straight_women$h12conform)

```

```{r restructuring}
# dyads <- Goldberg_gav_sm %>%
#   mutate(Partner = case_when(Partner == 1 ~ "A",
#                              Partner == 2 ~ "B")) %>%
#   gather(variable, value, group:n) %>%
#   unite(var_partner, variable, Partner) %>%
#   spread(var_partner, value)
# 
# small_dyad <- small %>%
#   mutate(gender = case_when(gender == -1 ~ "W",
#                             gender == 1 ~ "H")) %>%
#   select(-person) %>%
#   gather(variable, value, self1:self4)%>%
#   unite(var_gender, variable, gender) %>%
#   spread(var_gender, value) 

```


Report basic demographics for the sample. That is, percentages of gender,
percentages of racial groups, participant age, major, income, age of children,
adoption type, etc. This depends, of course, on what you have in your data. 

```{r demographics} 

#count how many dyads in each group type
Goldberg_gav_groups <- Goldberg_gav_sm %>%
  filter(Partner == 2) %>%
  group_by(group) %>%
  count()

#count how many people of each race
Goldberg_gav_sm$myrace_1[is.na(Goldberg_gav_sm$myrace_1)] <- 0
Goldberg_gav_sm$myrace_2[is.na(Goldberg_gav_sm$myrace_2)] <- 0
Goldberg_gav_sm$myrace_3[is.na(Goldberg_gav_sm$myrace_3)] <- 0
Goldberg_gav_sm$myrace_4[is.na(Goldberg_gav_sm$myrace_4)] <- 0
Goldberg_gav_sm$myrace_5[is.na(Goldberg_gav_sm$myrace_5)] <- 0
Goldberg_gav_sm$myrace_6[is.na(Goldberg_gav_sm$myrace_6)] <- 0
Goldberg_gav_sm$myrace_7[is.na(Goldberg_gav_sm$myrace_7)] <- 0

race <- Goldberg_gav_sm %>%
  select(contains("myrace"))

colSums(race)

race <- data.frame(column_name = colnames(race),
                   variable_label = get_label(race),
                   num_participants = colSums(race))

race <- race %>%
  mutate(perc_participants = (num_participants / 178) * 100)

#find level of education of participants
education <- Goldberg_gav_sm %>%
  group_by(educ) %>%
  count()

ed_labels <- data.frame(get_labels(Goldberg_gav_sm$educ))
data.table::setDT(ed_labels, keep.rownames = TRUE)[]
ed_labels$rn <- as.numeric(ed_labels$rn)

education <- education %>%
  left_join(ed_labels, by = c("educ" = "rn"))

names(education) <- c("educ", "num_participants", "level")
education <- education %>%
  mutate(perc_participants = (num_participants / 178) * 100)

#average relationship length
mean(lesbians$w11RelDur)
mean(gays$w11RelDur)
mean(straight_women$w11RelDur)
mean(straight_men$w11RelDur)

#sexual orientation
sexual_orientation <- Goldberg_gav_sm %>%
  select(ID, Partner, sexor, group) %>%
  group_by(sexor) %>%
  count()

sexor_labels <- data.frame(variable_label =
                           get_labels(Goldberg_gav_sm$sexor))
data.table::setDT(sexor_labels, keep.rownames = TRUE)[]
sexor_labels$rn <- as.numeric(sexor_labels$rn)
sexual_orientation <- sexual_orientation %>%
  left_join(sexor_labels, by = c("sexor" = "rn"))

#parent's age
parent_age <- Goldberg_gav_sm %>%
  select(ID, Partner, group, paraccme_5) %>%
  group_by(paraccme_5) %>%
  count()


```

```{r counts_labels}
counts_labels <- function(data, x) {
  #if factor convert to numeric
  dims <- dim(data)
  counts <- data %>%
    select_(x) %>%
    group_by_(x) %>%
    count_()
  labels <- tibble(variable_label = 
                     get_labels(data[[x]]))
  data.table::setDT(labels, keep.rownames = TRUE)[]
  labels$rn <- as.numeric(labels[,rn])
  names(counts)[1] <- "x"
  x_bins <- counts %>%
    right_join(labels, by = c("x" = "rn"))
  names(x_bins)[1] <- c(x, "n", "variable_label")
  x_bins[["n"]][is.na(x_bins[["n"]])] <- 0
  x_bins <- x_bins %>%
    mutate(percent = round((n / dims[[1]]) * 100))
  x_bins <- x_bins %>%
    select(1, variable_label, everything())
  return(x_bins)
}
```

```{r implement_counts_labels}
education_counts <- counts_labels(Goldberg_gav_sm, "educ")
sexor_counts <- counts_labels(Goldberg_gav_sm, "sexor")
#income_counts <- counts_labels(Goldberg_gav_sm, "faminc")

race_child <- counts_labels(Goldberg_gav_sm, "w12Race")
sjlabelled::get_label(Goldberg_gav_sm$paraccme_5)
counts_age <- counts_labels(Goldberg_gav_sm, "paraccme_5")
```

```{r faminc}
income <- skim(Goldberg_gav_sm$faminc)
#127 missings
#51 completes
# mean = 175327.5
#Q1 100000.0
#Q2 167000.0
#Q3 205000.0
#Q4 565000.0

childage_at_adoption <- skim(Goldberg_gav_sm$h12Age)
#THIS VARIABLE IS IN MONTHS
#mean = 	10.03
# sd = 23.45
# Q3 = 7, max = 144
```

```{r correlations}
corr.test(gays %>% select(SocComp, Prosocial, Emotional, h12social, h12selfdir, h12conform))
corr.test(lesbians %>% select(SocComp, Prosocial, Emotional, h12social, h12selfdir, h12conform))
corr.test(Goldberg_gav_sm %>% select(SocComp, Prosocial, Emotional, h12social, h12selfdir, h12conform))
corr.test(straight_women %>% select(SocComp, Prosocial, Emotional, h12social, h12selfdir, h12conform))
corr.test(straight_men %>% select(SocComp, Prosocial, Emotional, h12social, h12selfdir, h12conform))
```


```{r}
#Above the diagonal are lesbians, below the diagonal are gay males
corr_matrix1 <- tribble(
  ~"", ~"Social Competence", ~"Prosocial Competence", ~"Emotional Competence", ~"Social Values", ~"Self-Direction Values", ~"Conformity Values",
  "Social Competence",    "1.00",  "0.90*", "0.89*",  "0.09", "-0.01",  "0.19",
  "Prosocial Competence", "0.93*",  "1.00",  "0.60*", "0.11", "-0.01",  "0.23",
  "Emotional Competence", "0.95*", "0.76*",  "1.00",   "0.04", "-0.01",  "0.11",
  "Social Values",      "0.10",   "0.04",  "0.15",   "1.00", "-0.33",   "0.07",
  "Self-Direction Values","-0.06", "-0.07",  "0.05",  "-0.10",  "1.00", "-0.17",
  "Conformity Values",    "0.31",  "0.36",  "0.22",    "0.04", "-0.22",   "1.00"
  
)

knitr::kable(corr_matrix1, caption = "Table 1: Correlations. Women in same-sex couples are above the diagonal, men in same-sex couples are below the diagonal.")
```

```{r}
#Above the diagonal are the straight women, below the diagonal are straight men
corr_matrix2 <- tribble(
  ~"", ~"Social Competence", ~"Prosocial Competence", ~"Emotional Competence", ~"Social Values", ~"Self-Direction Values", ~"Conformity Values",
  "Social Competence",    "1.00",  "0.92*", "0.92*",  "0.04", "0.03",  "-0.23",
  "Prosocial Competence", "0.95*",  "1.00",  "0.70*", "-0.04", "0.11",  "-0.18",
  "Emotional Competence", "0.93*", "0.76*",  "1.00",   "0.12", "-0.06",  "-0.24",
  "Social Values",      "-0.23",   "-0.27",  "-0.15",  "1.00", "-0.22",  "0.16",
  "Self-Direction Values", "0.28", "0.26",    "0.26",  "-0.20",  "1.00",  "-0.03",
  "Conformity Values",    "-0.02",  "-0.08", "0.05",    "0.18", "0.21",      "1.00"
  
 )
knitr::kable(corr_matrix2, caption = "Table 2: Correlations. Women in heterosexual couples are above the diagonal, men in heterosexual couples are below the diagonal.")
```


```{r}
t.test(filter(gays, Partner == 1)[["w11RelDur"]], (filter(lesbians, Partner == 1)[["w11RelDur"]]))

t.test(straight_men$w11RelDur,filter(gays, Partner == 1)[["w11RelDur"]])

t.test(straight_women$w11RelDur,filter(lesbians, Partner == 1)[["w11RelDur"]])
  
```


Out of the `r dim(Goldberg_gav_sm)[1]` participants, `r dim(filter(Goldberg_gav_sm, gender == 1))[1]` are female and `r dim(filter(Goldberg_gav_sm, gender == 2))[1]` are male. `r sexor_counts[1, 4]`% identify as `r sexor_counts[1, 2]`, `r sexor_counts[2, 4]`% identify as `r sexor_counts[2, 2]`, `r sexor_counts[3, 4]`% identify as `r sexor_counts[3, 2]`, `r sexor_counts[4, 4]`% identify as `r sexor_counts[4, 2]`, `r sexor_counts[5, 4]`% identify as `r sexor_counts[5, 2]`, `r sexor_counts[6, 4]`% identify as `r sexor_counts[6, 2]`, and `r sexor_counts[7, 4]`% identify as `r sexor_counts[7, 2]`.


```{r}
t.test(gays$w11RelDur, lesbians$w11RelDur)
t.test(gays$w11RelDur, straight_women$w11RelDur)
t.test(gays$w11RelDur, straight_men$w11RelDur)
t.test(lesbians$w11RelDur, straight_women$w11RelDur)
t.test(lesbians$w11RelDur, straight_men$w11RelDur)
t.test(straight_women$w11RelDur, straight_men$w11RelDur)

rel_dur_model <- lm(w11RelDur ~ gender + group, data = Goldberg_gav_sm)
summary(rel_dur_model)

women_ed <- Goldberg_gav_sm %>%
  filter(gender == 1) %>%
  select(educ)
men_ed <- Goldberg_gav_sm %>%
  filter(gender == 2) %>%
  select(educ)
t.test(women_ed$educ, men_ed$educ)
t.test(gays$educ, lesbians$educ)
t.test(gays$educ, straight_women$educ)
t.test(gays$educ, straight_men$educ)
t.test(lesbians$educ, straight_women$educ)
t.test(lesbians$educ, straight_men$educ)
```

```{r}
education_counts <- counts_labels(Goldberg_gav_sm, "educ")
```
```{r}
qplot(w12Age, data = Goldberg_gav_sm)
```

