---
title: "Measures and Preliminary Analyses"
author:
- name: Alina Barylsky
- name: Gav Bell
- name: Emma Livingston
- name: Paige Salters
classoption: man
output:
  papaja::apa6_docx: default
  papaja::apa6_pdf: default
draft: no
figurelist: no
floatsintext: no
footnotelist: no
keywords: keywords
linenumbers: no
mask: no
documentclass: apa6
tablelist: no
bibliography: r-references.bib
---

```{r setup, include = FALSE}
library(papaja)
library(psysds364data)
library(tidyverse)
library(sjlabelled)
library(psych)
library(skimr)
data("Goldberg_gav")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
knitr::opts_chunk$set(include = FALSE)
options(tinytex.verbose = TRUE)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. 


# Preliminary Analyses

```{r variables}
var_labels <- data.frame(column_name = colnames(Goldberg_gav),
                         variable_label = sjlabelled::get_label(Goldberg_gav))

Goldberg_gav_sm <- Goldberg_gav %>%
  select(ID,
         Partner,
         group,
         ChildAge,
         chgend,
         gendexp,
         gender,
         sexor,
         w11RelDur,
         contains("chrace"),
         religion,
         howrelig,
         contains("otherch"),
         occup,
         contains("otherwork"),
         educ,
         faminc,
         paraccme_5,
         contains("polit"),
         contains("gayaff"),
         cityst,
         contains("genderparent"),
         sexor,
         contains("myrace"),
         contains("h12"),
         contains("w12"),
         h12social,
         h12selfdir,
         h12conform,
         contains("soccomp"),
         SocComp,
         Prosocial,
         Emotional
         )

```

```{r subset_data}
#exclude individuals who do not have data for parental values or social competence

#find the subset of dyads who have information for both people for all of the variables
Goldberg_gav_completes <- Goldberg_gav_sm %>%
  filter(!is.na(SocComp) & !is.na(Prosocial) & !is.na(Emotional) & !is.na(h12social) & !is.na(h12selfdir) & !is.na(h12conform)) %>%
  group_by(ID) %>%
  count() %>%
  filter(n == 2)

#join this subset with the full set of individuals
Goldberg_gav_sm <- Goldberg_gav_sm %>%
  inner_join(Goldberg_gav_completes, by = "ID")

```

```{r}
Goldberg_gav_sm %>%
  group_by(gender) %>%
  count()

Goldberg_gav_sm <- Goldberg_gav_sm %>%
  mutate(gender = ifelse(gender == 3, 1, gender))

Goldberg_gav_sm$gender[is.na(Goldberg_gav_sm$gender)] <- 1

Goldberg_gav_sm %>%
  group_by(gender) %>%
  count()

#impute ID 231 partner 2's relationship duration
Goldberg_gav_sm <- Goldberg_gav_sm %>%
  mutate(w11RelDur = ifelse(ID == 231 & Partner == 2, 7.0, w11RelDur))
  
```

```{r subset_by_group}
lesbians <- Goldberg_gav_sm %>%
  filter(group == 1)

gays <- Goldberg_gav_sm %>%
  filter(group == 2)

straight_men <- Goldberg_gav_sm %>%
  filter(group == 3 & gender == 2)

straight_women <- Goldberg_gav_sm %>%
  filter(group == 3 & gender == 1)
```

```{r averages}
mean(lesbians$SocComp)
mean(gays$SocComp)
mean(straight_men$SocComp)
mean(straight_women$SocComp)

mean(lesbians$h12conform)
mean(gays$h12conform)
mean(straight_men$h12conform)
mean(straight_women$h12conform)

```

```{r restructuring}
# dyads <- Goldberg_gav_sm %>%
#   mutate(Partner = case_when(Partner == 1 ~ "A",
#                              Partner == 2 ~ "B")) %>%
#   gather(variable, value, group:n) %>%
#   unite(var_partner, variable, Partner) %>%
#   spread(var_partner, value)
# 
# small_dyad <- small %>%
#   mutate(gender = case_when(gender == -1 ~ "W",
#                             gender == 1 ~ "H")) %>%
#   select(-person) %>%
#   gather(variable, value, self1:self4)%>%
#   unite(var_gender, variable, gender) %>%
#   spread(var_gender, value) 

```


Report basic demographics for the sample. That is, percentages of gender,
percentages of racial groups, participant age, major, income, age of children,
adoption type, etc. This depends, of course, on what you have in your data. 

```{r demographics} 

#count how many dyads in each group type
Goldberg_gav_groups <- Goldberg_gav_sm %>%
  filter(Partner == 2) %>%
  group_by(group) %>%
  count()

#count how many people of each race
Goldberg_gav_sm$myrace_1[is.na(Goldberg_gav_sm$myrace_1)] <- 0
Goldberg_gav_sm$myrace_2[is.na(Goldberg_gav_sm$myrace_2)] <- 0
Goldberg_gav_sm$myrace_3[is.na(Goldberg_gav_sm$myrace_3)] <- 0
Goldberg_gav_sm$myrace_4[is.na(Goldberg_gav_sm$myrace_4)] <- 0
Goldberg_gav_sm$myrace_5[is.na(Goldberg_gav_sm$myrace_5)] <- 0
Goldberg_gav_sm$myrace_6[is.na(Goldberg_gav_sm$myrace_6)] <- 0
Goldberg_gav_sm$myrace_7[is.na(Goldberg_gav_sm$myrace_7)] <- 0

race <- Goldberg_gav_sm %>%
  select(contains("myrace"))

colSums(race)

race <- data.frame(column_name = colnames(race),
                   variable_label = get_label(race),
                   num_participants = colSums(race))

race <- race %>%
  mutate(perc_participants = round((num_participants / 178), digits = 4) * 100)

#find level of education of participants
education <- Goldberg_gav_sm %>%
  group_by(educ) %>%
  count()

ed_labels <- data.frame(get_labels(Goldberg_gav_sm$educ))
data.table::setDT(ed_labels, keep.rownames = TRUE)[]
ed_labels$rn <- as.numeric(ed_labels$rn)

education <- education %>%
  left_join(ed_labels, by = c("educ" = "rn"))

names(education) <- c("educ", "num_participants", "level")
education <- education %>%
  mutate(perc_participants = (num_participants / 178) * 100)

#average relationship length
mean(lesbians$w11RelDur)
mean(gays$w11RelDur)
mean(straight_women$w11RelDur)
mean(straight_men$w11RelDur)

#sexual orientation
sexual_orientation <- Goldberg_gav_sm %>%
  select(ID, Partner, sexor, group) %>%
  group_by(sexor) %>%
  count()

sexor_labels <- data.frame(variable_label =
                           get_labels(Goldberg_gav_sm$sexor))
data.table::setDT(sexor_labels, keep.rownames = TRUE)[]
sexor_labels$rn <- as.numeric(sexor_labels$rn)
sexual_orientation <- sexual_orientation %>%
  left_join(sexor_labels, by = c("sexor" = "rn"))

#parent's age
parent_age <- Goldberg_gav_sm %>%
  select(ID, Partner, group, paraccme_5) %>%
  group_by(paraccme_5) %>%
  count()


```

```{r counts_labels}
counts_labels <- function(data, x) {
  #if factor convert to numeric
  dims <- dim(data)
  counts <- data %>%
    select_(x) %>%
    group_by_(x) %>%
    count_()
  labels <- tibble(variable_label = 
                     get_labels(data[[x]]))
  data.table::setDT(labels, keep.rownames = TRUE)[]
  labels$rn <- as.numeric(labels[,rn])
  names(counts)[1] <- "x"
  x_bins <- counts %>%
    right_join(labels, by = c("x" = "rn"))
  names(x_bins)[1] <- c(x, "n", "variable_label")
  x_bins[["n"]][is.na(x_bins[["n"]])] <- 0
  x_bins <- x_bins %>%
    mutate(percent = round((n / dims[[1]]), digits = 4) * 100)
  x_bins <- x_bins %>%
    select(1, variable_label, everything())
  return(x_bins)
}

```

```{r implement_counts_labels}
education_counts <- counts_labels(Goldberg_gav_sm, "educ")
sexor_counts <- counts_labels(Goldberg_gav_sm, "sexor")
#income_counts <- counts_labels(Goldberg_gav_sm, "faminc")

race_child <- counts_labels(Goldberg_gav_sm, "w12Race")
```

```{r faminc}
income <- skim(Goldberg_gav_sm$faminc)
#127 missings
#51 completes
# mean = 175327.5
#Q1 100000.0
#Q2 167000.0
#Q3 205000.0
#Q4 565000.0

childage_at_adoption <- skim(Goldberg_gav_sm$h12Age)
#THIS VARIABLE IS IN MONTHS
#mean = 	10.03
# sd = 23.45
# Q3 = 7, max = 144
```

```{r correlations}
corr.test(gays %>% select(SocComp, Prosocial, Emotional, h12social, h12selfdir, h12conform))
corr.test(lesbians %>% select(SocComp, Prosocial, Emotional, h12social, h12selfdir, h12conform))
corr.test(Goldberg_gav_sm %>% select(SocComp, Prosocial, Emotional, h12social, h12selfdir, h12conform))
corr.test(straight_women %>% select(SocComp, Prosocial, Emotional, h12social, h12selfdir, h12conform))
corr.test(straight_men %>% select(SocComp, Prosocial, Emotional, h12social, h12selfdir, h12conform))
```

```{r}
#Above the diagonal are lesbians, below the diagonal are gay males
corr_matrix1 <- tibble(
  c("Social Competence", "Prosocial Competence", "Emotional Competence", "Social Values", "Self-Direction Values", "Conformity Values"),
  c("1.00", "0.93*", "0.95*", "0.10", "-0.06", "0.31*"),
  c("0.9*", "1.00", "0.76*", "0.04", "-0.07", "0.36*"),
  c("0.89*", "0.60*", "1.00", "0.15", "-0.05", "0.22"),
  c("0.09", "0.11", "0.04", "1.00", "-0.10", "0.04"),
  c("-0.01", "-0.01", "-0.01", "-0.33*", "1.00", "-0.22"),
  c("0.19", "0.23", "0.11", "0.07", "-0.17", "1.00")
)

names(corr_matrix1) <- c("Social Competence", "Prosocial Competence", "Emotional Competence", "Social Values", "Self-Direction Values", "Conformity Values")

knitr::kable(corr_matrix1)
```


```{r relationship_ttest}
t.test(filter(gays, Partner == 1)[["w11RelDur"]], (filter(lesbians, Partner == 1)[["w11RelDur"]]))

t.test(straight_men$w11RelDur,filter(gays, Partner == 1)[["w11RelDur"]])

t.test(straight_women$w11RelDur,filter(lesbians, Partner == 1)[["w11RelDur"]])
  
```

The current sample includes `r dim(Goldberg_gav_sm)[1]` participants and `r dim(Goldberg_gav_sm)[1] / 2`, including `r dim(lesbians)[1] / 2` female same-sex couples, `r dim(gays)[1] / 2` male same-sex couples, and `r dim(straight_women)[1]` heterosexual couples. The sample was determined by excluding any participants who did not have data for the primary variables of interest: Parental Values and Social Competence. Thus, any dyad that does not have information from both partners in the relevant variables was excluded.

Out of the `r dim(Goldberg_gav_sm)[1]` participants, `r dim(filter(Goldberg_gav_sm, gender == 1))[1]` are female and `r dim(filter(Goldberg_gav_sm, gender == 2))[1]` are male. In this subset of participants, `r pluck(sexor_counts, 1, 4)`% (n = `r pluck(sexor_counts, 1, 3]`) identify as `r pluck(sexor_counts, 1, 2)`,  `r pluck(sexor_counts, 2, 4)`% (n = `r pluck(sexor_counts, 2, 3]`) identify as `r pluck(sexor_counts, 2, 2)`, `r pluck(sexor_counts, 3, 4)`% (n = `r pluck(sexor_counts, 3, 3]`) identify as `r pluck(sexor_counts, 3, 2)`,  `r pluck(sexor_counts, 4, 4)`% (n = `r pluck(sexor_counts, 4, 3]`) identify as `r pluck(sexor_counts, 4, 2)`, `r pluck(sexor_counts, 5, 4)`% (n = `r pluck(sexor_counts, 5, 3]`) identify as `r pluck(sexor_counts, 5, 2)`,  `r pluck(sexor_counts, 6, 4)`% (n = `r pluck(sexor_counts, 6, 3]`) identify as `r pluck(sexor_counts, 6, 2)`, and `r pluck(sexor_counts, 7, 4)`% (n = `r pluck(sexor_counts, 7, 3]`) identify as `r pluck(sexor_counts, 7, 2)`. 

fix race
This sample is rather well educated: `r education_counts[1, 4]`% (n = `education_counts[1, 3]`) have "`r education_counts[1, 4]`", `r education_counts[2, 4]`% (n = `education_counts[2, 3]`) have a "`r education_counts[2, 4]`", `r education_counts[3, 4]`% (n = `education_counts[3, 3]`) have "`r education_counts[3, 4]`", `r education_counts[4, 4]`% (n = `education_counts[4, 3]`) have a "`r education_counts[4, 4]`", `r education_counts[5, 4]`% (n = `education_counts[5, 3]`) have a "`r education_counts[5, 4]`", and `r education_counts[6, 4]`% (n = `education_counts[6, 3]`) have a "`r education_counts[6, 4]`".


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
